\LARGE \bf Generalizing Informed Sampling for Asymptotically-Optimal Sampling-based Kinodynamic Planning via Markov Chain Monte Carlo

### 2018-02-23 paper.tex
initial updates to sec VI

\begin{figure*}[t!]
	\centering
	\begin{subfigure}[t!]{0.325\textwidth}
		\centering
		\includegraphics[width=\textwidth]{fig/sampling_efficiency/levelset}
		\caption{\captionstyle The informed set volume ratio decrease as $ \cbest $ decreases in the planning process in different dimensions.}
		\label{fig:sampling_efficiency:levelset}
	\end{subfigure}
	\begin{subfigure}[t!]{0.325\textwidth}
		\centering
		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
		\caption{\captionstyle 4-dimension sampling space.}
		\label{fig:sampling_efficiency:2d}
	\end{subfigure}
	\begin{subfigure}[t!]{0.325\textwidth}
		\centering
		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
		\caption{\captionstyle 12-dimension sampling space.}
		\label{fig:sampling_efficiency:6d}
	\end{subfigure}
	\caption{\captionstyle Average sampling time vs informed set volume ratio of four samplers (RS, HRS, MH and HNR) in state spaces of different dimensions. 
	The X axis is the ratio of informed set volume to the entire sampling space.
	The Y axis is the average time per sample.}
	\label{fig:sampling_efficiency}
\end{figure*}

@@

To evaluate the planning efficiency of the samplers, we run them with the informed RRT* planner~\cite{GSB14} in position-velocity space with MTDI as steering function, on three different problems described below and shown in Fig.~\ref{fig:problems}. 
For each problem the start and goal states (positions and velocities) are known in the joint space. 
Joint velocities at start and goal are calculated from desired end-effector velocities using inverse kinematics before starting the planning. Table~\ref{tab:params} shows the parameters used in the problems.

@@

\subsubsection{Problem 1: 6 Dimension - 3 DoF Planar Manipulator}

The start and the goal states have zero velocities.
%The position boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ [-1,1] $.
Fig.~\ref{fig:planning_efficiency:3dof:example} shows the planned path.

\subsubsection{Problem 2: 12 Dimension - 6 DoF Snake Arm}

The objective is to hammer the end-effector into the wall while starting with zero velocity.
%The position boundary of each join is $[-\pi,\pi]$, the velocity boundary is $[-10,10]$, and the acceleration is $[-1,1]$.
Fig.~\ref{fig:planning_efficiency:6dof:example} shows the planned path.

\subsubsection{Problem 3: 14 Dimension - 7 DoF WAM Arm}

The objective is to quickly swing away a glass on a table using the right arm.
Fig.~\ref{fig:planning_efficiency:herb:example} shows a few steps of a planned path.

\begin{figure*}[t!]
	\centering
	\begin{subfigure}[b]{\textwidth}
	    \centering
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_1}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_2}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_3}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_4}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_5}
		\caption{\captionstyle Problem 1 : 3DOF planar arm move from a start to a goal while starting and ending with zero velocities.}
		\vspace{6pt}
		\label{fig:planning_efficiency:3dof:example}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
	    \centering
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_1}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_2}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_3}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_4}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_5}
		\caption{\captionstyle Problem 2 : 6DOF snake hammers the end-effector into the wall while starting with zero velocity.}
		\vspace{6pt}
		\label{fig:planning_efficiency:6dof:example}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
    \centering
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_1}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_2}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_3}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_4}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_5}
	\caption{Problem 3 : HERB sweeps a cup on a table, in which the right arm starts with zero velocity and ends with non-zero velocity.}
	\label{fig:planning_efficiency:herb:example}
	\end{subfigure}
	\caption{\captionstyle Three problems are used to evaluate planning efficiency.
	These problems are defined in state spaces of different dimensions and subject to different kinodynamics.}
	\label{fig:problems}
\end{figure*}

\begin{figure*}[t!]
	\centering
	\begin{subfigure}[b]{0.325\textwidth}
		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_general}
		\caption{\captionstyle Problem 1 - 6 Dimensions.}
		\label{fig:planning_efficiency:3dof:general}
	\end{subfigure}	
	\begin{subfigure}[b]{0.325\textwidth}
		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_hammering}
		\caption{\captionstyle Problem 2 - 12 Dimensions.}
		\label{fig:planning_efficiency:6dof:hammering}
	\end{subfigure}
	\begin{subfigure}[b]{0.325\textwidth}
	\includegraphics[width=\linewidth]{fig/planning_efficiency/herb_batting_efficiency}
	\caption{\captionstyle Problem 3 - 14 Dimensions.}
	\label{fig:planning_efficiency:herb:batting}
    \end{subfigure}
	\caption{\captionstyle Planning Efficiency of four different samplers (RS, HRS, MH and HNR) in three problems. 
	The X axis is the planning time. 
	The Y axis is the ratio of the current best and the optimal $ \cbest / c^*_{\rm best} $.}
	\label{fig:planning_efficiency}
\end{figure*}

@@

\section{Acknowledge}

>>>>

\begin{figure*}[t!]
	\centering
	\begin{subfigure}[t!]{0.325\textwidth}
		\centering
		\includegraphics[width=\textwidth]{fig/sampling_efficiency/levelset}
		\caption{\captionstyle The informed set volume ratio decrease as $ \cbest $ decreases in the planning process in different dimensions.}
		\label{fig:sampling_efficiency:levelset}
	\end{subfigure}
	\begin{subfigure}[t!]{0.325\textwidth}
		\centering
		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
		\caption{\captionstyle 4-dimensional state space.}
		\label{fig:sampling_efficiency:2d}
	\end{subfigure}
	\begin{subfigure}[t!]{0.325\textwidth}
		\centering
		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
		\caption{\captionstyle 12-dimensional state space.}
		\label{fig:sampling_efficiency:6d}
	\end{subfigure}
	\caption{\captionstyle Average sampling time vs informed set volume ratio of four samplers (RS, HRS, MH and HNR) in state spaces of different dimensions. 
	The $x$-axis is the ratio of the volume of informed set and the volume of the entire state space.
	The $y$-axis is the average time per sample.}
	\label{fig:sampling_efficiency}
\end{figure*}

@@

To evaluate the planning efficiency of the samplers, we run them with the informed RRT* planner~\cite{GSB14} in position-velocity space with MTDI as steering function, on three different problems described below and shown in Fig.~\ref{fig:problems}. 
For each problem the start and goal states (positions and velocities) are known in the joint space. 
Joint velocities at start and goal are calculated from desired end-effector velocities using inverse kinematics before starting the planning. Table~\ref{tab:params} shows the parameters used in the problems and Fig.~\ref{fig:problems} depicts the planned path for the three problems.

@@

\begin{enumerate}
	\item[\textbf{P1}] \emph{6 Dimensional 3 DoF planar manipulator}---The objective is to move the arm from a start to a goal state, both with zero velocities.

	\item[\textbf{P2}] \emph{12 Dimensional 6 DoF snake arm}	---The objective is to hammer the end-effector into the wall while starting with zero velocity.

	\item[\textbf{P3}] \emph{14 Dimensional 7 DoF WAM arm}---The objective is to  to quickly swing away a glass on a table using the right arm.
\end{enumerate}
%
%
%\subsubsection[\textbf{P1}]{\textbf{P1} 6 Dimension - 3 DoF Planar Manipulator}
%
%The start and the goal states have zero velocities.
%%The position boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ [-1,1] $.
%Fig.~\ref{fig:planning_efficiency:3dof:example} shows the planned path.
%
%\subsubsection{Problem 2: 12 Dimension - 6 DoF Snake Arm}
%
%The objective is to hammer the end-effector into the wall while starting with zero velocity.
%%The position boundary of each join is $[-\pi,\pi]$, the velocity boundary is $[-10,10]$, and the acceleration is $[-1,1]$.
%Fig.~\ref{fig:planning_efficiency:6dof:example} shows the planned path.
%
%\subsubsection{Problem 3: 14 Dimension - 7 DoF WAM Arm}
%
%The objective is to quickly swing away a glass on a table using the right arm.
%Fig.~\ref{fig:planning_efficiency:herb:example} shows a few steps of a planned path.

\begin{figure*}[t!]
	\centering
	\begin{subfigure}[b]{\textwidth}
	    \centering
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_1}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_2}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_3}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_4}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_5}
		\caption{\captionstyle Problem \textbf{P1} : 3DOF planar arm moving from a start state to a goal state, both with zero velocities.}
		\vspace{6pt}
		\label{fig:planning_efficiency:3dof:example}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
	    \centering
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_1}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_2}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_3}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_4}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_5}
		\caption{\captionstyle Problem \textbf{P2} : 6DOF snake hammers the end-effector into the wall while starting with zero velocity.}
		\vspace{6pt}
		\label{fig:planning_efficiency:6dof:example}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
    \centering
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_1}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_2}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_3}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_4}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_5}
	\caption{Problem \textbf{P3} : HERB sweeps a cup on a table, in which the right arm starts with zero velocity and ends with non-zero velocity.}
	\label{fig:planning_efficiency:herb:example}
	\end{subfigure}
	\caption{\captionstyle Three problems in different state spaces and subject to different dynamic constraints used to evaluate planning efficiency.}
	\label{fig:problems}
\end{figure*}

\begin{figure*}[t!]
	\centering
	\begin{subfigure}[b]{0.325\textwidth}
		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_general}
		\caption{\captionstyle Problem \textbf{P1} - 6 dimensions.}
		\label{fig:planning_efficiency:3dof:general}
	\end{subfigure}	
	\begin{subfigure}[b]{0.325\textwidth}
		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_hammering}
		\caption{\captionstyle Problem \textbf{P2} - 12 dimensions.}
		\label{fig:planning_efficiency:6dof:hammering}
	\end{subfigure}
	\begin{subfigure}[b]{0.325\textwidth}
	\includegraphics[width=\linewidth]{fig/planning_efficiency/herb_batting_efficiency}
	\caption{\captionstyle Problem \textbf{P3} - 14 dimensions.}
	\label{fig:planning_efficiency:herb:batting}
    \end{subfigure}
	\caption{\captionstyle Planning Efficiency of four different samplers (RS, HRS, MH and HNR) in three problems. 
	The $x$-axis is the planning time. 
	The $y$-axis is the ratio of the current best and the optimal $ \cbest / c^*_{\rm best} $.}
	\label{fig:planning_efficiency}
\end{figure*}

@@

\section{Acknowledgements}
